NGO Repression as a Predictor of Worsening Human Rights Abuses

### 2021-11-15 manuscript/manuscript.Rmd
Mention Egypt case study in intro roadmap
Address Reviewer 2's issue 9 about connection between CS and HR violations

Below, we first look at existing literature on repression and political violence, outlining state motivations to repress NGOs. We then elaborate on why attacking NGOs may be an important predictor of subsequent repression. Using both original data as well as data from several existing datasets, we build an ensemble of predictive models and explore (1) the marginal effects of civil society repression on different forms of broader human rights repression, and (2) the out-of-sample predictive performance of each model. We conclude by discussing the implications of our findings on autocratic survival, and how states may manage NGOs as a strategy to remain in power.

@@

This administrative crackdown via anti-NGO laws may foreshadow future government transgressions. Autocratic leaders want to avoid accountability, and NGOs often stand in conflict with that goal. Civil society organizations, including NGOs, can help shape the narrative of leaders' performance both domestically and internationally. Monitoring by NGOs and subsequent shaming can include significant external revenue loss to states in the form of loss of aid, trade, and foreign direct investments [@KeckSikkink:1998; @BarryClayFlynn:2013]. Government attempts to repress NGOs can signal the beginning of a deteriorating human rights situation. Such repression reflects the government's willingness and capability to use measures that can make it avoid accountability. Once a state targets NGOs, over time it may grow less hesitant to apply violent repression more widely and more severely.

>>>>

Below, we first look at existing literature on repression and political violence, outlining state motivations to repress NGOs. We then elaborate on why attacking NGOs may be an important predictor of subsequent repression. Using both original data as well as data from several existing datasets, we build an ensemble of predictive models and explore (1) the marginal effects of civil society repression on different forms of broader human rights repression, and (2) the out-of-sample predictive performance of each model. We then illustrate one of the mechanisms of our findings—the disconnect between de jure and de facto anti-NGO repression—with a brief case study of Egypt's treatment of civil society since 2002. We conclude by discussing the implications of our findings on autocratic survival, and how states may manage NGOs as a strategy to remain in power.

@@

This administrative crackdown via anti-NGO laws can provide convenient avenues for more violent repression and can foreshadow future government transgressions. Autocratic leaders want to avoid accountability and NGOs often stand in conflict with that goal. Civil society organizations, including NGOs, can help shape the narrative of leaders' performance both domestically and internationally. Monitoring by NGOs and subsequent shaming can include significant external revenue loss to states in the form of loss of aid, trade, and foreign direct investments [@KeckSikkink:1998; @BarryClayFlynn:2013]. Government attempts to repress NGOs can signal the beginning of a deteriorating human rights situation. Such repression reflects the government's willingness and capability to use measures that can make it avoid accountability. Once a state targets NGOs, over time it may grow less hesitant to apply violent repression more widely and more severely, thus leading to broader contractions of civil and human rights throughout the country.
